---
title: "Amanda_CooneyUSEMarkdownNotebook"
output:
  pdf_document: default
  html_document: default
date: "2024-08-01"
---

# Graphical and Statistical Analysis of Food and Animal Data using USE

This notebook details the analysis of Animal and Food VFT data of normal hearing (NH) individuals compared with prelingually deaf individuals with cochlear implants (CI), using Universal Sentence Encoder. Analysis includes three main levels of comparison: semantic similarity, frequency value, and phonological similarity.

## Initial Graphical Analysis of Food Data

This section compares the Food data of NH and CI individuals in regard to semantic similarity, frequency value, and phonological similarity. 

### Group Differences in Mean Semantic Similarity

```{r}
library(ggplot2)

data <- read.csv("~/Library/CloudStorage/OneDrive-BowdoinCollege/Desktop/lexicon lab/Grouped_Food_Summary_Stats_Data.csv", header = TRUE)

CI <- which(data$Group == "CI")
NH <- which(data$Group == "NH")

CI_sem <- data[CI,]$Semantic_Similarity_mean
NH_sem <- data[NH,]$Semantic_Similarity_mean

mean_sem <- c(mean(CI_sem),mean(NH_sem))
groups_sem <- c("CI","NH")

sem_df <- data.frame(Group = groups_sem, means = mean_sem)

sem_graph <- ggplot(sem_df, aes(x = Group, y = means, fill = Group)) +
  geom_bar(stat = "identity") +
  labs(x = "Hearing Status", y = "Mean Semantic Similarity", title = "Group Differences in Mean Semantic Similarity (Food Domain)") +
  coord_cartesian(ylim = c(0,0.5))
```

### Group Differences in Mean Frequency Value

```{r}
library(ggplot2)

data <- read.csv("~/Library/CloudStorage/OneDrive-BowdoinCollege/Desktop/lexicon lab/Grouped_Food_Summary_Stats_Data.csv", header = TRUE)

CI <- which(data$Group == "CI")
NH <- which(data$Group == "NH")

CI_freq <- data[CI,]$Frequency_Value_mean
NH_freq <- data[NH,]$Frequency_Value_mean

means <- c(mean(CI_freq),mean(NH_freq))
groups <- c("CI","NH")

freq_df <- data.frame(Group = groups,means = means)

freq_graph <- ggplot(freq_df, aes(x = Group, y = means, fill = Group)) +
  geom_bar(stat = "identity") + 
  labs(x = "Hearing Status", y = "Mean Frequency Value", title = "Group Differences in Mean Frequency Value (Food Domain)") +
  coord_cartesian(ylim = c(0,7))
```

### Group Differences in Mean Phonological Similiarity

```{r}
library(ggplot2)

data <- read.csv("~/Library/CloudStorage/OneDrive-BowdoinCollege/Desktop/lexicon lab/Grouped_Food_Summary_Stats_Data.csv", header = TRUE)

CI <- which(data$Group == "CI")
NH <- which(data$Group == "NH")

CI_phon <- data[CI,]$Values_Computed_from_Phonological_Means
NH_phon <- data[NH,]$Values_Computed_from_Phonological_Means

mean_phon <- c(mean(CI_phon, na.rm = TRUE),mean(NH_phon, na.rm = TRUE))
groups_phon <- c("CI","NH")

phon_df <- data.frame(Group = groups_phon, means = mean_phon)

phon_graph <- ggplot(phon_df, aes(x = Group, y = means, fill = Group)) +
  geom_bar(stat = "identity") +
  labs(x = "Hearing Status", y = "Mean Phonological Similarity", title = "Group Differences in Mean Phonological Similarity (Food Domain)") +
  coord_cartesian(ylim = c(0,0.125))
```

## Initial Graphical Analysis of Animal Data

This section compares the Animal data of NH and CI individuals in regard to semantic similarity, frequency value, and phonological similarity. 

### Group Differences in Mean Semantic Similarity

```{r}
data <- read.csv("~/Library/CloudStorage/OneDrive-BowdoinCollege/Desktop/lexicon lab/Grouped_Animal_Summary_Stats_Data.csv", header = TRUE)

#extracting specific data from larger csv file
CI <- which(data$Group =="CI")
CI_freq <- data[CI,]$Frequency_Value_mean

NH <-which(data$Group == "NH")
NH_freq <- data[NH,]$Frequency_Value_mean
means <- c(mean(CI_freq),mean(NH_freq))
groups <- c("CI","NH")

CI_sem <- data[CI,]$Semantic_Similarity_mean
NH_sem <- data[NH,]$Semantic_Similarity_mean

mean_sem <- c(mean(CI_sem),mean(NH_sem))
groups_sem <- c("CI","NH")

sem_df <- data.frame(Group = groups_sem, means = mean_sem)

sem_graph <- ggplot(sem_df, aes(x = Group, y = means, fill = Group)) +
  geom_bar(stat = "identity") +
  labs(x = "Hearing Status", y = "Mean Semantic Similarity", title = "Group Differences in Mean Semantic Similarity (Animal Domain)") +
  coord_cartesian(ylim = c(0,0.5))
```

### Group Differences in Mean Frequency Value

```{r}
data <- read.csv("~/Library/CloudStorage/OneDrive-BowdoinCollege/Desktop/lexicon lab/Grouped_Animal_Summary_Stats_Data.csv", header = TRUE)

#extracting specific data from larger csv file
CI <- which(data$Group =="CI")
CI_freq <- data[CI,]$Frequency_Value_mean

NH <-which(data$Group == "NH")
NH_freq <- data[NH,]$Frequency_Value_mean
means <- c(mean(CI_freq),mean(NH_freq))
groups <- c("CI","NH")

freq_df <- data.frame(Group = groups,means = means)

freq_graph <- ggplot(freq_df, aes(x = Group, y = means, fill = Group)) +
  geom_bar(stat = "identity") + 
  labs(x = "Hearing Status", y = "Mean Frequency Value", title = "Group Differences in Mean Frequency Value (Animal Domain)") +
  coord_cartesian(ylim = c(0,7))
```

### Group Differences in Mean Phonological Similarity

```{r}
data <- read.csv("~/Library/CloudStorage/OneDrive-BowdoinCollege/Desktop/lexicon lab/Grouped_Animal_Summary_Stats_Data.csv", header = TRUE)

#extracting specific data from larger csv file
CI <- which(data$Group =="CI")
CI_freq <- data[CI,]$Frequency_Value_mean

NH <-which(data$Group == "NH")
NH_freq <- data[NH,]$Frequency_Value_mean
means <- c(mean(CI_freq),mean(NH_freq))
groups <- c("CI","NH")

CI_phon <- data[CI,]$Phonological_Similarity_mean
NH_phon <- data[NH,]$Phonological_Similarity_mean

mean_phon <- c(mean(CI_phon),mean(NH_phon))
groups_phon <- c("CI","NH")

phon_df <- data.frame(Group = groups_phon, means = mean_phon)

phon_graph <- ggplot(phon_df, aes(x = Group, y = means, fill = Group)) +
  geom_bar(stat = "identity") +
  labs(x = "Hearing Status", y = "Mean Phonological Similarity", title = "Group Differences in Mean Phonological Similarity (Animal Domain)") +
  coord_cartesian(ylim = c(0,0.1))
```

### Scatterplot of Mean Phonological Similarity vs. Number of Items Generated

```{r}
data <- read.csv("~/Library/CloudStorage/OneDrive-BowdoinCollege/Desktop/lexicon lab/Grouped_Animal_Summary_Stats_Data.csv", header = TRUE)

#extracting specific data from larger csv file
CI <- which(data$Group =="CI")
CI_freq <- data[CI,]$Frequency_Value_mean

NH <-which(data$Group == "NH")
NH_freq <- data[NH,]$Frequency_Value_mean
means <- c(mean(CI_freq),mean(NH_freq))
groups <- c("CI","NH")

subset_data <- data[,c("Phonological_Similarity_mean","Number_of_Items", "Group")]
no_NA_data <- which(subset_data$Group != "NA")

scatterplot <- ggplot(subset_data[no_NA_data,], aes(x = Phonological_Similarity_mean, y = Number_of_Items, color=Group)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Mean Phonological Similarity", y = "Number of Items Generated", title = "Scatter plot of Mean Phonological Similarity vs. Number of Items Generated in NH and CI Individuals") +
  coord_cartesian(ylim = c(0,40))
```

## Refined Graphical and Statistical Analysis of Food and Animal Data

This section reflects a secondary round of analysis after replacements for previous exclusions were made to the vocabularies programmed into USE.

### Group Differences in Mean Semantic Similarity

```{r}
library(ggplot2)

animal_data <- read.csv("~/Library/CloudStorage/OneDrive-BowdoinCollege/Desktop/lexicon lab/FinalAnimalDescStats_Grouped.csv")

CI_animals <- which(animal_data$Group == "CI")
NH_animals <- which(animal_data$Group == "NH")

CI_animals_sem <- animal_data[CI_animals,]$Semantic_Similarity_mean
NH_animals_sem <- animal_data[NH_animals,]$Semantic_Similarity_mean

animal_mean_sem <- c(mean(CI_animals_sem),mean(NH_animals_sem))
groups_sem <- c("CI","NH")

CI_animals_sem_std <- animal_data[CI_animals,]$Semantic_Similarity_std
NH_animals_sem_std <- animal_data[NH_animals,]$Semantic_Similarity_std

animal_mean_std <- c(mean(CI_animals_sem_std),mean(NH_animals_sem_std))

animal_df <- data.frame(Group = groups_sem, means = animal_mean_sem, stdv = animal_mean_std, Domain = "Animals")

food_data <- read.csv("~/Library/CloudStorage/OneDrive-BowdoinCollege/Desktop/lexicon lab/FinalFoodDescStats_Grouped.csv")

CI_foods <- which(food_data$Group == "CI")
NH_foods <- which(food_data$Group == "NH")

CI_food_sem <- food_data[CI_foods,]$Semantic_Similarity_mean
NH_food_sem <- food_data[NH_foods,]$Semantic_Similarity_mean

food_mean_sem <- c(mean(CI_food_sem),mean(NH_food_sem))
groups_sem <- c("CI","NH")

CI_foods_sem_std <- food_data[CI_foods,]$Semantic_Similarity_std
NH_foods_sem_std <- food_data[NH_foods,]$Semantic_Similarity_std

food_mean_std <- c(mean(CI_foods_sem_std),mean(NH_foods_sem_std))

food_df <- data.frame(Group = groups_sem, means = food_mean_sem, stdv = food_mean_std, Domain = "Foods")

combined_df <- rbind(food_df, animal_df)

refined_sem_graph <- ggplot(combined_df, aes(x = Domain, y = means, fill = Group)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(aes(ymin = means - stdv, ymax = means + stdv), 
                width = 0.2,
                position = position_dodge(width = 0.9)) +
  labs(x = "Hearing Status", y = "Mean Semantic Similarity", title = "Group Differences in Mean Semantic Similarity")

#performing t-test for mean semantic similarity of NH in Animal vs. Food Domain
t_test_result <- t.test(NH_animals_sem,NH_food_sem)
print(t_test_result)

#performing t-test for mean semantic similarity of CI in Animal vs. Food Domain
t_test_result <- t.test(CI_animals_sem,CI_food_sem)
print(t_test_result)

#performing t-test for mean semantic similarity between CI and NH in Animal Domain
t_test_result <- t.test(CI_animals_sem,NH_animals_sem)
print(t_test_result)

#performing t-test for mean semantic similarity between CI and NH in Food Domain 
t_test_result <- t.test(CI_food_sem,NH_food_sem)
print(t_test_result)

```

### Group Differences in Mean Frequency Value

```{r}
library(ggplot2)

animal_data <- read.csv("~/Library/CloudStorage/OneDrive-BowdoinCollege/Desktop/lexicon lab/FinalAnimalDescStats_Grouped.csv")

CI_animals <- which(animal_data$Group == "CI")
NH_animals <- which(animal_data$Group == "NH")

CI_animals_freq <- animal_data[CI_animals,]$Frequency_Value_mean
NH_animals_freq <- animal_data[NH_animals,]$Frequency_Value_mean

animal_means_freq <- c(mean(CI_animals_freq),mean(NH_animals_freq))
groups <- c("CI","NH")

CI_animals_sem_std <- animal_data[CI_animals,]$Frequency_Value_std
NH_animals_sem_std <- animal_data[NH_animals,]$Frequency_Value_std

animal_mean_std <- c(mean(CI_animals_sem_std),mean(NH_animals_sem_std))

animal_freq_df <- data.frame(Group = groups, means = animal_means_freq, stdv = animal_mean_std, Domain = "Animals")

food_data <- read.csv("~/Library/CloudStorage/OneDrive-BowdoinCollege/Desktop/lexicon lab/FinalFoodDescStats_Grouped.csv")

CI_foods <- which(food_data$Group == "CI")
NH_foods <- which(food_data$Group == "NH")

CI_food_freq <- food_data[CI_foods,]$Frequency_Value_mean
NH_food_freq <- food_data[NH_foods,]$Frequency_Value_mean

food_means_freq <- c(mean(CI_food_freq),mean(NH_food_freq))
groups <- c("CI","NH")

CI_foods_sem_std <- food_data[CI_foods,]$Frequency_Value_std
NH_foods_sem_std <- food_data[NH_foods,]$Frequency_Value_std

food_mean_std <- c(mean(CI_foods_sem_std),mean(NH_foods_sem_std))

food_freq_df <- data.frame(Group = groups, means = food_means_freq, stdv = food_mean_std, Domain = "Foods")

combined_df <- rbind(food_freq_df, animal_freq_df)

refined_freq_graph <- ggplot(combined_df, aes(x = Domain, y = means, fill = Group)) +
  geom_bar(stat = "identity", position = "dodge") + 
  geom_errorbar(aes(ymin = means - stdv, ymax = means + stdv), 
                width = 0.2,
                position = position_dodge(width = 0.9)) +
  labs(x = "Hearing Status", y = "Mean Frequency Value", title = "Group Differences in Mean Frequency Value")

#performing t-test for mean frequency value of NH in Animal vs. Food Domain
t_test_result <- t.test(NH_animals_freq,NH_food_freq)
print(t_test_result)

#performing t-test for mean frequency value of CI in Animal vs. Food Domain
t_test_result <- t.test(CI_animals_freq,CI_food_freq)
print(t_test_result)

#performing t-test for mean frequency value between CI and NH in Animal Domain
t_test_result <- t.test(CI_animals_freq,NH_animals_freq)
print(t_test_result)

#performing t-test for mean frequency value between CI and NH in Food Domain 
t_test_result <- t.test(CI_food_freq,NH_food_freq)
print(t_test_result)

`                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                               ### Group Differences in Mean Frequency Value

```{r}
library(ggplot2)

animal_data <- read.csv("~/Library/CloudStorage/OneDrive-BowdoinCollege/Desktop/lexicon lab/FinalAnimalDescStats_Grouped.csv")

CI_animals <- which(animal_data$Group == "CI")
NH_animals <- which(animal_data$Group == "NH")

CI_animals_freq <- animal_data[CI,]$Frequency_Value_mean
NH_animals_freq <- animal_data[NH,]$Frequency_Value_mean

animal_means_freq <- c(mean(CI_animals_freq),mean(NH_animals_freq))
groups <- c("CI","NH")

CI_animals_sem_std <- animal_data[CI,]$Frequency_Value_std
NH_animals_sem_std <- animal_data[NH,]$Frequency_Value_std

animal_mean_std <- c(mean(CI_animals_sem_std),mean(NH_animals_sem_std))

animal_freq_df <- data.frame(Group = groups, means = animal_means_freq, stdv = animal_mean_std, Domain = "Animals")

food_data <- read.csv("~/Library/CloudStorage/OneDrive-BowdoinCollege/Desktop/lexicon lab/FinalFoodDescStats_Grouped.csv")

CI_foods <- which(food_data$Group == "CI")
NH_foods <- which(food_data$Group == "NH")

CI_food_freq <- food_data[CI,]$Frequency_Value_mean
NH_food_freq <- food_data[NH,]$Frequency_Value_mean

food_means_freq <- c(mean(CI_food_freq),mean(NH_food_freq))
groups <- c("CI","NH")

CI_foods_sem_std <- food_data[CI,]$Frequency_Value_std
NH_foods_sem_std <- food_data[NH,]$Frequency_Value_std

food_mean_std <- c(mean(CI_foods_sem_std),mean(NH_foods_sem_std))

food_freq_df <- data.frame(Group = groups, means = food_means_freq, stdv = food_mean_std, Domain = "Foods")

combined_df <- rbind(food_freq_df, animal_freq_df)

refined_freq_graph <- ggplot(combined_df, aes(x = Domain, y = means, fill = Group)) +
  geom_bar(stat = "identity", position = "dodge") + 
  geom_errorbar(aes(ymin = means - stdv, ymax = means + stdv), 
                width = 0.2,
                position = position_dodge(width = 0.9)) +
  labs(x = "Hearing Status", y = "Mean Frequency Value", title = "Group Differences in Mean Frequency Value")

#performing t-test for mean frequency value of NH in Animal vs. Food Domain
t_test_result <- t.test(NH_animals_freq,NH_food_freq)
print(t_test_result)

#performing t-test for mean frequency value of CI in Animal vs. Food Domain
t_test_result <- t.test(CI_animals_freq,CI_food_freq)
print(t_test_result)

#performing t-test for mean frequency value between CI and NH in Animal Domain
t_test_result <- t.test(CI_animals_freq,NH_animals_freq)
print(t_test_result)

#performing t-test for mean frequency value between CI and NH in Food Domain 
t_test_result <- t.test(CI_food_freq,NH_food_freq)
print(t_test_result)

```

### Group Differences in Mean Phonological Similarity

```{r}
library(ggplot2)

animal_data <- read.csv("~/Library/CloudStorage/OneDrive-BowdoinCollege/Desktop/lexicon lab/FinalAnimalDescStats_Grouped.csv")

CI_animals <- which(animal_data$Group == "CI")
NH_animals <- which(animal_data$Group == "NH")

CI_animals_phon <- animal_data[CI,]$Phonological_Similarity_mean
NH_animals_phon <- animal_data[NH,]$Phonological_Similarity_mean

animal_mean_phon <- c(mean(CI_animals_phon, na.rm = TRUE),mean(NH_animals_phon, na.rm = TRUE))
groups_phon <- c("CI","NH")

CI_animals_sem_std <- animal_data[CI,]$Phonological_Similarity_std
NH_animals_sem_std <- animal_data[NH,]$Phonological_Similarity_std

animal_mean_std <- c(mean(CI_animals_sem_std),mean(NH_animals_sem_std))

animal_phon_df <- data.frame(Group = groups_phon, means = animal_mean_phon, stdv = animal_mean_std, Domain = "Animals")

food_data <- read.csv("~/Library/CloudStorage/OneDrive-BowdoinCollege/Desktop/lexicon lab/FinalFoodDescStats_Grouped.csv")

CI_foods <- which(food_data$Group == "CI")
NH_foods <- which(food_data$Group == "NH")

CI_foods_phon <- food_data[CI,]$Phonological_Similarity_mean
NH_foods_phon <- food_data[NH,]$Phonological_Similarity_mean

food_mean_phon <- c(mean(CI_foods_phon, na.rm = TRUE),mean(NH_foods_phon, na.rm = TRUE))
groups_phon <- c("CI","NH")

CI_foods_sem_std <- food_data[CI,]$Phonological_Similarity_std
NH_foods_sem_std <- food_data[NH,]$Phonological_Similarity_std

food_mean_std <- c(mean(CI_foods_sem_std),mean(NH_foods_sem_std))

food_phon_df <- data.frame(Group = groups_phon, means = food_mean_phon, stdv = food_mean_std, Domain = "Foods")

combined_df <- rbind(food_phon_df, animal_phon_df)

refined_phon_graph <- ggplot(combined_df, aes(x = Domain, y = means, fill = Group)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(aes(ymin = means - stdv, ymax = means + stdv), 
                width = 0.2,
                position = position_dodge(width = 0.9)) +
  labs(x = "Hearing Status", y = "Mean Phonological Similarity", title = "Group Differences in Mean Phonological Similarity")

#performing t-test for mean phonological similarity of NH in Animal vs. Food Domain
t_test_result <- t.test(NH_animals_phon,NH_foods_phon)
print(t_test_result)

#performing t-test for mean phonological similarity of CI in Animal vs. Food Domain
t_test_result <- t.test(CI_animals_phon,CI_foods_phon)
print(t_test_result)

#performing t-test for mean phonological similarity between CI and NH in Animal Domain
t_test_result <- t.test(CI_animals_phon,NH_animals_phon)
print(t_test_result)

#performing t-test for mean phonological similarity between CI and NH in Food Domain 
t_test_result <- t.test(CI_foods_phon,NH_foods_phon)
print(t_test_result)

```

