---
title: "Cochlear Analysis"
author: "Channing Hambric"
date: "2025-02-10"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Set up 
## Libraries
```{r}
library(tidyverse)
library(ggthemes)
library(purrr)
library(ggpubr)
library(lubridate)
library(dplyr)
library(ggplot2)
library(tidyboot)
library(gridExtra)
library(lme4)
library(emmeans)
library(data.table)
library(knitr)
library(kableExtra)
library(uuid)
library(paletteer)
library(ggh4x)
library(geomtextpath)
library(ggbeeswarm)
library(rcartocolor)
library(patchwork)
library(ggridges)
library(forcats)
library(broom)
library(data.table)
```

## Define Data Import & Validation Functions

```{r}

domains <- c("animals", "foods")  
models <- c("word2vec", "speech2vec", "USE", "blended")
dimensions <- c("50", "100", "200", "300", "512")
alphas <- c("0.0", "0.1", "0.2", "0.3", "0.4", "0.5", "0.6", "0.7", "0.8", "0.9", "1.0")

# Function to read and process files
read_model_data <- function(file_type, domain, model, dimension, alpha) {
  valid_file_types <- c("lexical_results.csv", "model_results.csv", 
                        "individual_descriptive_stats.csv", "switch_results.csv")
  
  if (!(file_type %in% valid_file_types)) {
    stop(sprintf("Invalid file_type: %s. Choose from: %s", file_type, paste(valid_file_types, collapse = ", ")))
  }
  
  file_path <- sprintf("../output/%s/%s/%s/%s/%s", domain, model, dimension, alpha, file_type)
  
  if (file.exists(file_path)) {
    read.csv(file_path) %>%
      mutate(domain = domain,      
             dimension = as.character(dimension),
             structure = model,
             alpha = alpha,
             file_type = file_type)  # Track which file type this row comes from
  } else {
    NULL
  }
}

# Function to combine multiple datasets based on file type
combine_model_data <- function(file_type) {
  map_dfr(domains, function(domain) {
    map_dfr(models, function(model) {
      map_dfr(dimensions, function(dimension) {
        map_dfr(alphas, function(alpha) {
          read_model_data(file_type, domain, model, dimension, alpha)
        })
      })
    })
  })
}

# Function to validate row counts by structure, dimension, and alpha for each domain
validate_combined_data <- function(combined_data, file_type) {
  # Load individual domain datasets
  animals_data <- combined_data %>% filter(domain == "animals")
  foods_data <- combined_data %>% filter(domain == "foods")
  
  # Group and count rows for each combination of structure, dimension, and alpha
  animals_counts <- animals_data %>% count(structure, dimension, alpha, name = "count")
  foods_counts <- foods_data %>% count(structure, dimension, alpha, name = "count")
  
  # Check if counts are equal within each domain
  animals_valid <- all(animals_counts$count == animals_counts$count[1])
  foods_valid <- all(foods_counts$count == foods_counts$count[1])
  
  # Stop execution if counts are inconsistent within domains
  if (!animals_valid) {
    print("❌ Row count mismatch in 'animals' data for some combinations:")
    print(animals_counts)
    stop("Animals data has inconsistent row counts across structure-dimension-alpha combinations.")
  }
  
  if (!foods_valid) {
    print("❌ Row count mismatch in 'foods' data for some combinations:")
    print(foods_counts)
    stop("Foods data has inconsistent row counts across structure-dimension-alpha combinations.")
  }
  
  # Total row count validation
  total_rows_check <- (nrow(animals_data) + nrow(foods_data)) == nrow(combined_data)
  
  if (!total_rows_check) {
    stop("❌ Total row count mismatch: Sum of individual domain rows does not match the combined dataset.")
  }
  
  message(sprintf("✅ Validity check passed for %s: Row counts are consistent within each domain and total sum matches!", file_type))
}


```

## Import & Restructure Data

```{r}
#For assigning CI/NH status 
participant_groupings <- read.csv("../participant_groupings.csv")

#import data
#lexical results
full_lexical_data <- combine_model_data("lexical_results.csv") %>%select(-file_type)%>%left_join(participant_groupings)

#check_data
validate_combined_data(full_lexical_data, "lexical_results.csv")

#indv descrp stats
#takes a few sec
full_indv_data <- combine_model_data("individual_descriptive_stats.csv") %>%select(-file_type)%>%left_join(participant_groupings) %>% rename("fluency_score"="X._of_Items")%>%separate(Switch_Method, 
           into = c("method", "param1", "param2", "param3"), #separating out parameters
           sep = "_", 
           fill = "right")%>%mutate(full_method=paste(method,param1,param2,param3,sep="_"))
#check data
validate_combined_data(full_indv_data, "individual_descriptive_stats.csv")

#model results
#Takes a few min
full_model_data <- combine_model_data("model_results.csv") %>%select(-file_type)%>%left_join(participant_groupings) %>%
  separate(Model, 
           into = c("forage", "foraging_type", "method", "param1", "param2", "param3"), #separating out model parameters
           sep = "_", 
           fill = "right") %>%
  mutate(
    forage = factor(forage),
    foraging_type = factor(foraging_type),
    method = factor(method),
    param1 = factor(param1),
    param2 = factor(param2),
    param3 = factor(param3),
    dimension = factor(dimension),
    alpha = factor(alpha))%>%
  mutate(model_type = fct_recode(foraging_type, 
                                  `pstatic` = "phonologicalstatic", #renaming models
                                  `plocal` = "phonologicaldynamiclocal",
                                  `pglobal` = "phonologicaldynamicglobal",
                                  `pswitch` = "phonologicaldynamicswitch",
                                  `static` = "static", 
                                  `dynamic` = "dynamic", 
                                  `random` = "random")) %>%
  mutate(full_method=paste(method,param1,param2,param3,sep="_"))%>%
  mutate(full_model=paste(model_type,full_method,sep="_"))%>%
    mutate(full_speech=paste(structure,dimension,alpha,sep="_"))%>%
  mutate(everything=paste(full_model,full_speech,sep="_"))

#check data
validate_combined_data(full_model_data, "model_results.csv")

#switch designations
#A LOT OF DATA - using data.table
full_switch_data <- combine_model_data("switch_results.csv")%>%select(-file_type)
#Convert to data.table
setDT(full_switch_data)
setDT(participant_groupings)
#join with labels
full_switch_data <- participant_groupings[full_switch_data, on = "Subject"]  
#separate params
full_switch_data[, c("method", "param1", "param2", "param3") := tstrsplit(Switch_Method, "_", fixed = TRUE, fill = "NA")]
full_switch_data[, full_method := paste(method, param1, param2, param3, sep = "_")]
#convert back
full_switch_data<-as.data.frame(full_switch_data)
#check data
validate_combined_data(full_switch_data, "switch_results.csv")

```
# Analyses

## Lexical Analyses
```{r}
#note these values are the same across model variations
#setting up the df
lexical_analysis_data<-full_indv_data %>% select(Subject, Group, Semantic_Similarity_mean, Phonological_Similarity_mean, Frequency_Value_mean, 
         fluency_score, domain) %>% na.omit() %>%
  rename("semantic" = "Semantic_Similarity_mean", 
         "phonological" = "Phonological_Similarity_mean",
         "frequency" = "Frequency_Value_mean")%>%
  pivot_longer(names_to = "cue", cols=c(semantic,phonological,frequency))%>%mutate(Group = factor(Group, levels = c("NH","CI")))


#Does fluency score differ by Group and domain
fluency_lm = lm(data = lexical_analysis_data, fluency_score ~ Group*domain)
summary(fluency_lm)
car::Anova(fluency_lm)
emmeans(fluency_lm, pairwise~Group*domain, pbkrtest.limit = 38553)


#Does semantic similarity, phonological similarity, and frequency differ across Group x domain, fluency score as covariate
# Run lm() for each cue and extract results
lexical_results <- lexical_analysis_data  %>%
  group_by(cue) %>%                                   # Group by cue
  nest() %>%                                         # Nest data by cue
 mutate(
    model = map(data, ~ lm(value ~ Group * domain * fluency_score, data = .)) # Fit models
  )
#View results
model_summaries <- lexical_results %>%
  mutate(model_summary = map(model, broom::tidy)) %>%
  unnest(model_summary)
View(model_summaries)

```

### Fluency plot
```{r}
fluency_plot <- lexical_analysis_data %>%
  ggplot(aes(x = domain, y = fluency_score, fill = Group)) +
  geom_boxplot(color = "black") +
  ylim(0, 50) +  
  labs(y = 'Fluency score', x = "Domain", title = "") +
  theme_few() +
  theme(
    aspect.ratio = 1, axis.text.y = element_text(size = 14),axis.text.x = element_text(size = 14),
    legend.position = 'right',
    plot.title = element_text(size = 18)  
  ) +
  scale_fill_paletteer_d("LaCroixColoR::Mango") 

fluency_plot
```

### Lexical plots
```{r}
#plots
plots_lexical <- lexical_results %>% 
  mutate(
    emmip_plot = map(model, ~ 
      emmip(.x, Group ~ fluency_score | domain,  # Use Group for color, domain for facetting
            cov.reduce = range, CI = TRUE) +
      labs(title = "", x = "Fluency score", y = paste("Linear prediction", "(", unique(cue), ")")) +facet_wrap(~ domain) 
      +scale_colour_paletteer_d("LaCroixColoR::Mango") +
      theme_few() + 
      theme(aspect.ratio = 1.5, legend.position = "top")))


plots_lexical$emmip_plot[[1]]+plots_lexical$emmip_plot[[2]]+plots_lexical$emmip_plot[[3]]

```
### Semantic Similarity Across Structures
```{r}
plot_data<-full_indv_data %>%select(Subject, Group, Semantic_Similarity_mean, Phonological_Similarity_mean, Frequency_Value_mean, structure, dimension,alpha,
         fluency_score, domain) %>% na.omit() %>%mutate(Group = factor(Group, levels = c("NH","CI")))%>%mutate(dimension = factor(dimension, levels = c("50","100","200","300","512")))%>%mutate(structure = factor(structure, levels = c("word2vec","speech2vec","blended","USE")))


single<-plot_data %>% filter(structure!="blended") %>%
  ggplot(aes(x = structure, y = dimension, fill = Semantic_Similarity_mean)) +
  geom_tile() +
  scale_fill_gradient(low = "lightgoldenrod2", high = "red", name = "Avg Semantic Similarity") +
  labs(x = "", y = "Dimensions", title = "Single Model Stucture") +
  theme(legend.position="bottom",
    aspect.ratio = 1,
    plot.title = element_text(hjust = 0.5, size = rel(1.2)),
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
  facet_grid(Group ~ domain)

blended<-plot_data %>% filter(structure=="blended") %>%
  ggplot(aes(x = alpha, y = dimension, fill = Semantic_Similarity_mean)) +
  geom_tile() +
  scale_fill_gradient(low = "lightgoldenrod2", high = "red", name = "Avg Semantic Similarity") +
  labs(x = "alpha", y = "Dimensions", title = "Hybrid Model Stucture") +
  theme(legend.position="none",
    aspect.ratio = 1,
    plot.title = element_text(hjust = 0.5, size = rel(1.2)),
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
  facet_grid(Group ~ domain)
single+blended
```


## Model Analyses

## Best Model for Each Specific Group x Domain - nLL
```{r}
#Aggregate sum_nLLs across participants for each model variation for each Group in each domain
model_results = full_model_data %>%
  group_by(Group,domain,full_method,full_model,full_speech,everything) %>%
  summarise(sum_nLL = sum(Negative_Log_Likelihood_Optimized)) %>%
  arrange(sum_nLL) %>%ungroup()%>%
  group_by(Group,domain) %>%
  arrange(sum_nLL) %>%       
  slice(1) %>% 
  ungroup() %>%
  select(Group,domain,sum_nLL,full_method,full_model,full_speech,everything)
#print best models
kable(model_results)


#Excluding USE
no_USE_model_results = full_model_data %>%filter(structure!="USE") %>%
  group_by(Group,domain,full_method,full_model,full_speech,everything) %>%
  summarise(sum_nLL = sum(Negative_Log_Likelihood_Optimized)) %>%
  arrange(sum_nLL) %>%ungroup()%>%
  group_by(Group,domain) %>%
  arrange(sum_nLL) %>%       
  slice(1) %>% 
  ungroup() %>%
  select(Group,domain,full_method,full_model,full_speech,everything,sum_nLL)
#print best models
kable(no_USE_model_results)

```

## Best Model for Each Specific Group x Domain - BIC
```{r}
#Getting N
just_fluency<-full_indv_data %>%select(Subject,Group,domain,fluency_score) %>%rename("N"="fluency_score") %>%na.omit() %>%unique()
# Extract random model's NLL for each Subject x domain
random_nLL_lookup <- full_model_data %>%
  group_by(Subject,domain,Group,structure,dimension,alpha)%>%
  filter(model_type == "random") %>%
  select(Subject,domain,Group,structure,dimension,alpha, random_nLLs = Negative_Log_Likelihood_Optimized)


bic <- full_model_data %>%
  left_join(just_fluency, by = c("Subject", "Group", "domain")) %>%
  left_join(random_nLL_lookup, by = c("Subject","domain","Group","structure","dimension","alpha")) %>%  
  mutate(
    k = case_when(
      str_detect(full_model, "static|dynamic_norms|dynamic_simdrop|pstatic|plocal_norms|plocal_simdrop|pglobal_norms|pglobal_simdrop|pswitch_norms|pswitch_simdrop") ~ 5,
      str_detect(full_model, "dynamic_delta|plocal_delta|pglobal_delta|pswitch_delta") ~ 6,
      TRUE ~ 7  # multimodal delta
    ),
    optimalBIC = k * log(N) - 2 * Negative_Log_Likelihood_Optimized,
    randomBIC = k * log(N) - 2 * (-random_nLLs))

median_bic = bic %>% 
  mutate(deltaBIC  = randomBIC - optimalBIC) %>%
  group_by(Group,domain,everything) %>%
  summarise(medianBIC = median(deltaBIC)) %>%
  arrange(medianBIC) %>%
  slice(1) %>% 
  ungroup() 
kable(median_bic)
```


## Salience Parameter (Beta) Analyses
```{r}
#Filtering full data to only include best model for each domain type
best_models <- full_model_data %>%mutate(Group = factor(Group, levels = c("NH","CI")))%>%
  filter(paste(Group,domain,everything) %in% paste(model_results$Group, model_results$domain, model_results$everything)) %>%
  group_by(Group,domain)

#Separating out betas
beta_values  = best_models  %>%
  pivot_longer(names_to = "beta", cols = c(Beta_Frequency, Beta_Phonological, Beta_Semantic))


# Run lm() for each beta type and extract results
beta_results <- beta_values  %>%
  group_by(beta) %>%                                   
  nest() %>%                                         
 mutate(
    model = map(data, ~ lm(value ~ Group*domain, data = .)) 
  )

#View results
beta_summaries <- beta_results %>%
  mutate(model_summary = map(model, broom::tidy)) %>%
  unnest(model_summary)
View(beta_summaries)

```

### Beta plot

```{r}
beta_values %>%
  group_by(Group, domain, beta) %>%
  tidyboot_mean(value, nboot = 1000, na.rm = TRUE) %>%
  separate(beta, into = c("b", "beta")) %>%
  mutate(
    beta = tolower(beta),
    beta = fct_recode(beta, 
                      `Semantic\nSimilarity` = "semantic", 
                      `Phonological\nSimilarity` = "phonological",
                      `Word\nFrequency` = "frequency")
  ) %>%
  mutate(beta = fct_relevel(beta, "Semantic\nSimilarity", "Phonological\nSimilarity", "Word\nFrequency")) %>%
  ggplot(aes(x = beta, y = empirical_stat, group = Group, fill = Group)) + facet_wrap(~domain)+
  geom_bar(stat = 'identity', position = "dodge") +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0, position = position_dodge(0.9)) +
  labs(y = bquote(beta ~ "(Parameter Salience)"), x = "") +
  theme_few() +
  theme() +
  scale_fill_paletteer_d("LaCroixColoR::Mango")
```

## Clustering Analyses
```{r}
#filtering to only include best method from above
best_clusters <- full_indv_data %>%mutate(Group = factor(Group, levels = c("NH","CI")))%>%
  filter(paste(Group,domain, full_method) %in% paste(best_models$Group,best_models$domain, best_models$full_method)) %>%select(-fluency_score)%>% #this is full of NAs & produces mismatch .x/.y error, so dropping
  group_by(Group,domain) %>%left_join(lexical_analysis_data%>%select(Subject,Group,domain,fluency_score)%>%unique(), by = c("Subject", "Group","domain")) #adding fluency_score back in

#When using the best method for each Group x domain, does avg cluster mean differ by Group x domain
#number of items produced as a covariate
domain_cluster_size_lm = lm(data = best_clusters, Cluster_Size_mean ~ Group * domain * fluency_score)
summary(domain_cluster_size_lm)
car::Anova(domain_cluster_size_lm)
emmeans(domain_cluster_size_lm,pairwise~Group*domain,simple="Group")


#When using the best method for each Group x domain, does avg numb switches differ by Group x domain
domain_switch_numb_lm = lm(data = best_clusters, Number_of_Switches ~Group * domain * fluency_score)
summary(domain_switch_numb_lm)
car::Anova(domain_switch_numb_lm)
emmeans(domain_switch_numb_lm,pairwise~Group*domain,simple="Group")

```

### Cluster Plots
```{r}
#cluster size
clusters<-emmip(domain_cluster_size_lm,Group ~ fluency_score | domain, cov.reduce = range, CI = TRUE) + 
  guides(color = guide_legend(title = NULL)) +
  theme_few() + facet_wrap(~domain)+
  scale_colour_paletteer_d("LaCroixColoR::Mango") +
  labs(
    x = "Fluency score",
    y = "Predicted cluster size") +theme(aspect.ratio=.75,legend.position="right")

#number of switches
switches<-emmip(domain_switch_numb_lm, Group ~ fluency_score | domain, cov.reduce = range,CI=TRUE)+ 
      guides(color = guide_legend(title = NULL)) + facet_wrap(~domain)+ 
      theme_few() + scale_colour_paletteer_d("LaCroixColoR::Mango") +
  labs(
    x = "Fluency score",
    y = "Predicted number of switches")+theme(aspect.ratio=.75)

clusters+switches+ plot_layout(ncol = 1)
```

## Within Cluster vs Switch Analyses
```{r}
##SOMETHING WERID WITH JOINING - FIX - I THINK I JUST NEED TO ADD/DEL STRUCTURE DIM AND ALPHA
#filtering to only include best method for each domain
best_switches <- full_switch_data %>% select(-structure,-dimension,-alpha)%>%
  filter(paste(Group,domain,full_method) %in% paste(best_models$Group, best_models$domain, best_models$full_method)) %>%
  mutate(Switch_Value = if_else(Switch_Value == 2, 1, Switch_Value))

test<-best_switches%>%filter(domain=="animals")%>%filter(Group=="CI")
#Calculate item_no consistently in all_lexical to use in joining
items_lexical_data <- full_lexical_data %>%select(-structure,-dimension,-alpha)%>%
  group_by(Subject, Group, domain) %>%
  mutate(row_id = row_number() - 1)  # Adjust row_id to start at 0 to account for first item

#this code drops the first item from each list, and if switch_value = 1, marked as a switch trial, if switch_value=1, marked as within cluster transition, also labels clusters and switches by ordinal position
#new first item only marked as within cluster if original switch_value==0
switches_recoded <- best_switches %>%
  group_by(Subject,Group,domain) %>%
  mutate(
    Cluster_Number = cumsum(Switch_Value == 1),
    Switch = case_when(
      row_number() == 1 ~ "Within Cluster Transition",  # Changed to "Within Cluster Transition"
      Cluster_Number != lag(Cluster_Number) ~ "Switch Trial", # Adding cluster number
      TRUE ~ "Within Cluster Transition"
    )
  ) %>%
  mutate(Switch_Number = case_when(
    Switch == "Switch Trial" ~ Cluster_Number - 1,  # Adding switch number
    TRUE ~ NA_real_
  )) %>%
  group_by(Subject,Group, domain) %>%
  mutate(row_id = row_number() - 1) %>%  # Adjusting row_id to start at 0 to be able to drop first item
  left_join(items_lexical_data, by = c("Subject","Group", "Fluency_Item", "domain","row_id")) %>%
  rename(
    "semantic" = "Semantic_Similarity",
    "phonological" = "Phonological_Similarity",
    "frequency" = "Frequency_Value"
  ) %>% filter(row_id!=0)%>% #dropping first word of each list
  pivot_longer(names_to = "cue", cols = c(semantic, phonological, frequency))


## does cluster/switch designation predict semantic similarity, phonological similarity, and frequency for each Group x Domain
# Run lmer() for each cue type and extract results

switch_results <- switches_recoded  %>%
  group_by(cue) %>%                                   
  nest() %>%                                         
 mutate(
    model = map(data, ~ lm(value ~ Group*domain*Switch, data = .)) 
  )

#View results
#large so calling indp
print("Semantic")
switch_results$model[[1]] %>% summary()
print("phonological")
switch_results$model[[2]] %>% summary()
print("Frequency")
switch_results$model[[3]] %>% summary()

#phonology
emmeans(switch_results$model[[2]],pairwise~Group*domain*Switch,simple="Switch",pbkrtest.limit = 35657)
```


### Within/Across Cluster plots
```{r}
# Takes a long time w dyplr, converting to data.table
setDT(switches_recoded)

# Configure plots
plot_configs <- list(
  list(cue = "semantic", value_col = "value", y_label = "Semantic similarity", plot_title = ""),
  list(cue = "phonological", value_col = "value", y_label = "Phonological similarity", plot_title = ""),
  list(cue = "frequency", value_col = "value", y_label = "Word frequency", plot_title = "")
)

# Generate plots
wiac_cluster_plots <- map(plot_configs, ~ {
  data_subset <- switches_recoded[cue == .x$cue]
  
  data_subset[, Switch := fifelse(.x$cue == "frequency" & is.na(Switch), 
                                  "Cluster Transition", Switch)]
  
 data_subset[, Switch := factor(Switch, levels = c("Within Cluster Transition", "Switch Trial"))]
  
  # Convert back to tibble for tidyboot
  data_subset_tibble <- as_tibble(data_subset)
  
  boot_summary <- data_subset_tibble %>%
    group_by(domain, Switch, Group) %>%
    tidyboot_mean(!!sym(.x$value_col), nboot = 1000, na.rm = TRUE)

  # Plot 
  ggplot(boot_summary, aes(fill = Switch, y = empirical_stat, x = Group)) +
    facet_wrap(~domain) +
    geom_bar(stat = "identity", position = "dodge") +
   geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0.05, position = position_dodge(0.9)) +
   labs(
      title = .x$plot_title,
      y = .x$y_label,
      x = "",
      color = ""
  ) +
    theme_few() +
    theme(
      aspect.ratio = 1.5,
      legend.position = "top",
      axis.text.x = element_text(hjust = 1)
    ) +
   scale_fill_manual(values = c("cadetblue3", "orchid"))
})

wiac_cluster_plots[[1]] 
wiac_cluster_plots[[2]]  
wiac_cluster_plots[[3]]


#NOT TIDYBOOT
# Generate plots
wiac_cluster_plots <- map(plot_configs, ~ {
  data_subset <- switches_recoded[cue == .x$cue]
  
  data_subset[, Switch := fifelse(.x$cue == "frequency" & is.na(Switch), 
                                  "Cluster Transition", Switch)]
  
  data_subset[, Switch := factor(Switch, levels = c("Within Cluster Transition", "Switch Trial"))]
  
  # Compute means and standard errors (SE) instead of bootstrapped CIs
  summary_data <- data_subset[, .(
    mean_value = mean(get(.x$value_col), na.rm = TRUE),
    se = sd(get(.x$value_col), na.rm = TRUE) / sqrt(.N)
  ), by = .(domain, Switch, Group)]
  
  # Compute confidence intervals (assuming normal approximation)
  summary_data[, `:=`(ci_lower = mean_value - 1.96 * se,
                      ci_upper = mean_value + 1.96 * se)]

  # Plot 
  ggplot(summary_data, aes(fill = Switch, y = mean_value, x = Group)) +
    facet_wrap(~domain) +
    geom_bar(stat = "identity", position = "dodge") +
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0.05, position = position_dodge(0.9)) +
    labs(
      title = .x$plot_title,
      y = .x$y_label,
      x = "",
      color = ""
    ) +
    theme_few() +
    theme(
      aspect.ratio = 1.5,
      legend.position = "top",
      axis.text.x = element_text(hjust = 1)
    ) +
    scale_fill_manual(values = c("cadetblue3", "orchid"))
})

wiac_cluster_plots[[1]]
wiac_cluster_plots[[2]] 
wiac_cluster_plots[[3]]

```



