---
title: "Cochlear Analysis"
author: "Channing Hambric"
date: "2025-02-10"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Set up 
## Libraries
```{r}
library(tidyverse)
library(ggthemes)
library(purrr)
library(ggpubr)
library(lubridate)
library(dplyr)
library(ggplot2)
library(tidyboot)
library(gridExtra)
library(lme4)
library(emmeans)
library(data.table)
library(knitr)
library(kableExtra)
library(uuid)
library(paletteer)
library(ggh4x)
library(geomtextpath)
library(ggbeeswarm)
library(rcartocolor)
library(patchwork)
library(ggridges)
library(forcats)
library(broom)
library(data.table)
library(ggstats)
library(scales)
library(gt)
library(gtsummary)
```

## Define Data Import & Validation Functions

```{r}

domains <- c("animals", "foods")  
models <- c("word2vec", "speech2vec", "USE", "blended")
dimensions <- c("50", "100", "200", "300", "512")
alphas <- c("0.0", "0.1", "0.2", "0.3", "0.4", "0.5", "0.6", "0.7", "0.8", "0.9", "1.0")

# Function to read and process files
read_model_data <- function(file_type, domain, model, dimension, alpha) {
  valid_file_types <- c("lexical_results.csv", "model_results.csv", 
                        "individual_descriptive_stats.csv", "switch_results.csv")
  
  if (!(file_type %in% valid_file_types)) {
    stop(sprintf("Invalid file_type: %s. Choose from: %s", file_type, paste(valid_file_types, collapse = ", ")))
  }
  
  file_path <- sprintf("../output/%s/%s/%s/%s/%s", domain, model, dimension, alpha, file_type)
  
  if (file.exists(file_path)) {
    read.csv(file_path) %>%
      mutate(domain = domain,      
             dimension = as.character(dimension),
             structure = model,
             alpha = alpha,
             file_type = file_type)  # Track which file type this row comes from
  } else {
    NULL
  }
}

# Function to combine multiple datasets based on file type
combine_model_data <- function(file_type) {
  map_dfr(domains, function(domain) {
    map_dfr(models, function(model) {
      map_dfr(dimensions, function(dimension) {
        map_dfr(alphas, function(alpha) {
          read_model_data(file_type, domain, model, dimension, alpha)
        })
      })
    })
  })
}

# Function to validate row counts by structure, dimension, and alpha for each domain
validate_combined_data <- function(combined_data, file_type) {
  # Load individual domain datasets
  animals_data <- combined_data %>% filter(domain == "animals")
  foods_data <- combined_data %>% filter(domain == "foods")
  
  # Group and count rows for each combination of structure, dimension, and alpha
  animals_counts <- animals_data %>% count(structure, dimension, alpha, name = "count")
  foods_counts <- foods_data %>% count(structure, dimension, alpha, name = "count")
  
  # Check if counts are equal within each domain
  animals_valid <- all(animals_counts$count == animals_counts$count[1])
  foods_valid <- all(foods_counts$count == foods_counts$count[1])
  
  # Stop execution if counts are inconsistent within domains
  if (!animals_valid) {
    print("❌ Row count mismatch in 'animals' data for some combinations:")
    print(animals_counts)
    stop("Animals data has inconsistent row counts across structure-dimension-alpha combinations.")
  }
  
  if (!foods_valid) {
    print("❌ Row count mismatch in 'foods' data for some combinations:")
    print(foods_counts)
    stop("Foods data has inconsistent row counts across structure-dimension-alpha combinations.")
  }
  
  # Total row count validation
  total_rows_check <- (nrow(animals_data) + nrow(foods_data)) == nrow(combined_data)
  
  if (!total_rows_check) {
    stop("❌ Total row count mismatch: Sum of individual domain rows does not match the combined dataset.")
  }
  
  message(sprintf("✅ Validity check passed for %s: Row counts are consistent within each domain and total sum matches!", file_type))
}


```

## Import & Restructure Data

```{r}
#For assigning CI/NH status 
participant_groupings <- read.csv("../participant_groupings.csv")

#import data
#lexical results
full_lexical_data <- combine_model_data("lexical_results.csv") %>%select(-file_type)%>%left_join(participant_groupings)

#check_data
validate_combined_data(full_lexical_data, "lexical_results.csv")

#indv descrp stats
#takes a few sec
full_indv_data <- combine_model_data("individual_descriptive_stats.csv") %>%select(-file_type)%>%left_join(participant_groupings) %>% rename("fluency_score"="X._of_Items")%>%separate(Switch_Method, 
           into = c("method", "param1", "param2", "param3"), #separating out parameters
           sep = "_", 
           fill = "right")%>%mutate(full_method=paste(method,param1,param2,param3,sep="_"))
#check data
validate_combined_data(full_indv_data, "individual_descriptive_stats.csv")

#model results
#Takes a few min
full_model_data <- combine_model_data("model_results.csv") %>%select(-file_type)%>%left_join(participant_groupings) %>%
  separate(Model, 
           into = c("forage", "foraging_type", "method", "param1", "param2", "param3"), #separating out model parameters
           sep = "_", 
           fill = "right") %>%
  mutate(
    forage = factor(forage),
    foraging_type = factor(foraging_type),
    method = factor(method),
    param1 = factor(param1),
    param2 = factor(param2),
    param3 = factor(param3),
    dimension = factor(dimension),
    alpha = factor(alpha))%>%
  mutate(model_type = fct_recode(foraging_type, 
                                  `pstatic` = "phonologicalstatic", #renaming models
                                  `plocal` = "phonologicaldynamiclocal",
                                  `pglobal` = "phonologicaldynamicglobal",
                                  `pswitch` = "phonologicaldynamicswitch",
                                  `static` = "static", 
                                  `dynamic` = "dynamic", 
                                  `random` = "random")) %>%
  mutate(full_method=paste(method,param1,param2,param3,sep="_"))%>%
  mutate(full_model=paste(model_type,full_method,sep="_"))%>%
    mutate(full_speech=paste(structure,dimension,alpha,sep="_"))%>%
  mutate(everything=paste(full_model,full_speech,sep="_"))

#check data
validate_combined_data(full_model_data, "model_results.csv")

#switch designations
#A LOT OF DATA - using data.table
full_switch_data <- combine_model_data("switch_results.csv")%>%select(-file_type)
#Convert to data.table
setDT(full_switch_data)
setDT(participant_groupings)
#join with labels
full_switch_data <- participant_groupings[full_switch_data, on = "SID"]  
#separate params
full_switch_data[, c("method", "param1", "param2", "param3") := tstrsplit(Switch_Method, "_", fixed = TRUE, fill = "NA")]
full_switch_data[, full_method := paste(method, param1, param2, param3, sep = "_")]
#convert back
full_switch_data<-as.data.frame(full_switch_data)
#check data
validate_combined_data(full_switch_data, "switch_results.csv")

```
#===================================================Analysis Starts Here=========================================================

# Basic Fluency
```{r}
#Getting N
just_fluency<-full_indv_data %>%select(SID,Group,domain,fluency_score) %>%rename("N"="fluency_score") %>%na.omit() %>%unique()%>%  filter(!(SID %in% c("332053124","722249212","826471010","934821408","566255711","588241255")))

# basic fluency performance
# getting fluency means
just_fluency %>%
  group_by(Group) %>%
  summarise(
    mean_fluency = mean(N),
    sd_fluency = sd(N),
    N = n())

#Does fluency score differ by Group and domain
fluency_lm = lm(data = just_fluency, N ~ Group*domain)
summary(fluency_lm)
car::Anova(fluency_lm)
```

# Model Analyses

```{r}

#Extract random model's nLL for each SID x domain x structure x dim x alpha
random_nLL_lookup <- full_model_data %>%
  group_by(SID, domain, Group, structure, dimension, alpha) %>%
  filter(model_type == "random") %>%
  mutate(random_k = ifelse(structure == "blended", 2, 1)) %>% #setting random model k's
  select(SID, domain, Group, structure, dimension, alpha, random_k, 
         random_nLLs = Negative_Log_Likelihood_Optimized)


#setting up parameter matching
full_model_data_parameters<-full_model_data %>%mutate(parameter_link=paste(model_type,method,sep="_"))%>% filter(!(SID %in% c("332053124","722249212","826471010","934821408","566255711","588241255")))#exclude missing demos and atypical subjs

#importing parameter counts
parameters<-read.csv("BICparams_noswitch.csv") %>%select(parameter_link,k)

#calculating BIC
bic <- full_model_data_parameters %>%
  left_join(just_fluency, by = c("SID", "Group", "domain")) %>%
  left_join(random_nLL_lookup, by = c("SID","domain","Group","structure","dimension","alpha")) %>%  
  left_join(parameters, by="parameter_link") %>%
  mutate(
    optimalBIC = k * log(N) - 2 * (-Negative_Log_Likelihood_Optimized),
    randomBIC = random_k * log(N) - 2 * (-random_nLLs)) 

#dropping unused structures and switch methods
bic_clean<-bic %>%filter(structure == "blended", method =="multimodaldelta",dimension=="50", model_type!="random")


#best delta BIC model per participant - Use
best_blended_delta_bic = bic_clean%>% 
  group_by(SID,Group,domain) %>%
  mutate(deltaBIC  = randomBIC - optimalBIC)%>%
  arrange(desc(deltaBIC)) %>%
  slice(1)


#Getting SID counts
best_blended_delta_bic %>%
  group_by(Group, domain) %>%
  summarise(Unique_SIDs = n_distinct(SID), .groups = "drop")


# is there support for assuming a patchy structure
# how well do static models fit

#bic_clean_static<-bic %>%filter(structure == "blended",dimension=="50", model_type!="random")

#best delta BIC model per participant incl static
#best_blended_delta_bic_static = bic_clean_static%>% 
#  group_by(SID,Group,domain) %>%
#  mutate(deltaBIC  = randomBIC - optimalBIC)%>%
#  arrange(desc(deltaBIC)) %>%
#  slice(1)
#none with best fit static model

```

## Looking at Model Distributions
```{r}
#set up df
#make sure alphas are numeric
best_blended_delta_bic_analysis <- best_blended_delta_bic %>%
  mutate(
    Group = factor(Group, levels = c("NH", "CI")),
    param1 = ifelse(param1 %in% c("categorical", "associative"), NA_real_, 
                    as.numeric(gsub("alpha=", "", param1))),
    alpha = as.numeric(as.character(alpha)),
    method = as.character(method),model_type = as.character(model_type))

#=============================STRUCTURAL ALPHA====================================================

#comparing proportions of indv w specific alphas
#collapsing across domains, looking at maximal weighting of s2v
alpha_test <- best_blended_delta_bic_analysis 
alpha_table <- table(alpha_test$Group,alpha_test$alpha)

#look at tables to get counts
# Number with alpha = 1.0
nh_1.0 <- 3    
ci_1.0 <- 12   

# Total in each group
nh_total <- 53  
ci_total <- 46  

#2 proportion z test - 1.0
prop.test(x = c(nh_1.0, ci_1.0), n = c(nh_total, ci_total), correct = FALSE)
#sig more CIs

#just for animals domain
animals_alpha_test <- best_blended_delta_bic_analysis %>%
  filter(domain == "animals")
alpha_animals_table <- table(animals_alpha_test$Group, animals_alpha_test$alpha)

#look at tables to get counts
# Number with alpha = 1.0
nh_1.0 <- 2    
ci_1.0 <- 6   

# Total in each group
nh_animals_total <- 29  
ci_animals_total <- 29  

#2 proportion z test - 1.0
prop.test(x = c(nh_1.0, ci_1.0), n = c(nh_animals_total, ci_animals_total), correct = FALSE)
#ns

#just for foods domain
foods_alpha_test <- best_blended_delta_bic_analysis %>%
  filter(domain == "foods")
alpha_foods_table <- table(foods_alpha_test$Group, foods_alpha_test$alpha)

#look at tables to get counts
# Number with alpha = 1.0
nh_1.0 <- 1    
ci_1.0 <- 6   

# Number with alpha = 0.0 - no s2v
nh_0.0 <- 6    
ci_0.0 <- 6   

# Total in each group
nh_foods_total <- 24  
ci_foods_total <- 17  

#2 proportion z test - 1.0
prop.test(x = c(nh_1.0, ci_1.0), n = c(nh_foods_total, ci_foods_total), correct = FALSE)
#sig more for CI

#2 proportion z test - 0.0
prop.test(x = c(nh_0.0, ci_0.0), n = c(nh_foods_total, ci_foods_total), correct = FALSE)
#ns

### Does age of implantation or length of use correlate w/ best-fit structural alpha
# Note demographic information & individual battery scores are not publicly available due to confidentiality concerns.

#import data
#library(tableone)
#demos<-read.csv("demographics.csv")

#demos_clean<-demos %>% select(ID,Group,Gender,NIH_Race,CAYRS2,Eti,FitMOS,UseYRS2,X.4ppvtae) %>%filter(!(ID %in% c("754", "159")))%>%
#  rename(
#  Race = NIH_Race,
#  Age = CAYRS2,
#  Etiology = Eti,
 # PPVT=X.4ppvtae)

# for table
#demos_NH<-demos_clean%>%filter(Group=="NH") %>% select(ID,Group,Gender,Age,Race)%>%mutate(
#    Etiology = NA_character_,
#    `Age of Implantation (in Months)` = NA_real_,
#    `Length of Use` = NA_real_)

#demos_CI<-demos_clean%>%filter(Group=="CI")
#demos_combined<-rbind(demos_NH,demos_CI)%>%rename(SID="ID")


# does structural alpha correlate w/ age of implantation / years of use
#alpha_implant <- best_blended_delta_bic_analysis %>%
#  filter(Group == "CI") %>%
#  select(SID, Group, domain, alpha) %>%             
#  rename(ID = SID) %>%
#  mutate(
#   ID = as.character(stringr::str_sub(ID, 5)),
#    alpha = as.numeric(alpha)
#  ) %>%
#  left_join(
#    demos_CI %>%
#      mutate(ID = as.character(ID)),
#    by = c("ID", "Group")
 # ) 

# plot age of implantation x alpha
#ggplot(
#  data = alpha_implant,
#  aes(
#    x = FitMOS,
#    y = alpha,
#    color = domain,
#    group = domain
#  )
#) +
#  facet_wrap(~ domain) +
#  theme_few() +
#  geom_point(size = 2, alpha = 0.7) +
#  geom_smooth(method = "lm", se = TRUE, size = 1) +
#  scale_y_continuous(breaks = seq(0, 1, by = 0.10)) +   # <-- increments of .10
#  theme(
#    aspect.ratio = 1,
#    axis.text.x = element_text(hjust = 1, face = "bold")
#  ) +
#  paletteer::scale_colour_paletteer_d("nationalparkcolors::CraterLake") +
#  labs(y = "structural alpha", x = "age of implantation (months)")

# plot length of use x alpha
#ggplot(
#  data = alpha_implant,
#  aes(
#    x = UseYRS2,
#    y = alpha,
#    color = domain,
#    group = domain
#  )
#) +
#  facet_wrap(~ domain) +
#  theme_few() +
#  geom_point(size = 2, alpha = 0.7) +
#  geom_smooth(method = "lm", se = TRUE, size = 1) +
#  scale_y_continuous(breaks = seq(0, 1, by = 0.10)) +   # <-- increments of .10
#  theme(
#    aspect.ratio = 1,
#    axis.text.x = element_text(hjust = 1, face = "bold")
# ) +
#  paletteer::scale_colour_paletteer_d("nationalparkcolors::CraterLake") +
#  labs(y = "structural alpha", x = "length of use (years)")


# does length of use or age of implantation predict alpha
#alpha_corr<- lm(data=alpha_implant, alpha~domain*UseYRS2*FitMOS)
#summary(alpha_corr) 

## BATTERY MEASURES

## Group differences in receptive semantic processing via PPVT

# get group averages for PPVT
#demos_clean %>%
#  group_by(Group) %>%
#  summarise(
 #   mean_PPVT = mean(PPVT),
 #   sd_PPVT = sd(PPVT))


#ppvt<- lm(data=demos_clean, PPVT~Group)
#summary(ppvt)


### Does phonological processing ability, measured by nonword repetition score, differ by group

#import NWR data
#nwr_data<-read.csv("nwr_data.csv")
#nwr_comp<-best_blended_delta_bic_analysis %>%left_join(nwr_data)%>%filter(NWR_Score!="#NULL!")%>%mutate(NWR_Score=as.numeric(NWR_Score))

#Group averages
#nwr_comp %>%
#  group_by(Group) %>%
#  summarise(
#    mean_nwr = mean(NWR_Score),
#    sd_fluency = sd(NWR_Score))


#nwr<- lm(data=nwr_comp, NWR_Score~Group)
#summary(nwr)


#==============SWITCH PARAMETERS=======================

#comparing multimodal switch betas across domains, collapsing across groups
domain_mm_test=best_blended_delta_bic_analysis 
domain_mm_table <- table(domain_mm_test$domain, domain_mm_test$param1)

# Number with beta < 0.5
animals_switch_beta <- 2    
foods_switch_beta <- 19  

# Total in each group
animals_total <- 58  
foods_total <- 41  

# Run 2 proportion z test
prop.test(x = c(animals_switch_beta,foods_switch_beta), n = c(animals_total, foods_total), correct = FALSE)
#foods more likely to have a lower mm alpha

#comparing multimodal betas across groups in foods, do more CIs ignore phonology (Beta = 1)
group_mm_test=best_blended_delta_bic_analysis %>%
  filter(domain == "foods")
group_mm_table <- table(group_mm_test$Group, group_mm_test$param1)

# Number with mm beta = 1
nh_foods_switch_beta <- 2    
ci_foods_switch_beta <- 10  

# Run 2 proportion z test
prop.test(x = c(nh_foods_switch_beta,ci_foods_switch_beta), n = c(nh_foods_total, ci_foods_total), correct = FALSE)


#======================MODELS============================

#do more NHs have a best-fit model that includes phonology, collapsing across domains
group_model_table <- table(best_blended_delta_bic_analysis$Group, best_blended_delta_bic_analysis$model_type)

# Number with phon models
nh_phon_models <-37    
ci_phon_models <-21    

# Total in each group
nh_model_total <- 53 
ci_model_total <- 46  

# Run 2 proportion z test
prop.test(x = c(nh_phon_models,ci_phon_models), n = c(nh_model_total, ci_model_total), correct = FALSE)
#NHs sig more likely to have phon models

#looking at pswitch in foods
model_test=best_blended_delta_bic_analysis %>%
  filter(domain == "foods")
model_table <- table(model_test$Group, model_test$model_type)

# Number with pswitch
nh_pswitch <- 8    
ci_pswitch <- 1   

# Total in each group
nh_foods_total <- 24  
ci_foods_total <- 17  

# Run 2 proportion z test
prop.test(x = c(nh_pswitch,ci_pswitch), n = c(nh_foods_total, ci_foods_total), correct = FALSE)
#NHs sig more likely to have pswitch model


```
 


## Individual Differences Plots
```{r}
#nested bar plots

palette <- paletteer::paletteer_d("colorBlindness::Blue2Green14Steps")
switch_palette <- palette[-1]
scale_fill_custom <- scale_fill_manual(values = switch_palette)

#STRUCTURE
#Looking at structural alphas
structure_prop <- best_blended_delta_bic_analysis %>% 
  mutate(alpha = as.character(alpha)) %>%
  group_by(Group, domain) %>%
  count(Group, domain, alpha, name = "n") %>%
  mutate(prop = n / sum(n)) %>%
  ungroup()

ggplot(structure_prop, aes(x = Group, y = prop, fill = alpha)) +
  geom_col(position = position_dodge(width = 0.8), width = 0.75) +
  facet_wrap(~ domain) +
  scale_y_continuous(
    labels = percent_format(accuracy = 1),
    limits = c(0, 0.4),       
    expand = expansion(mult = c(0, 0.05))
  ) +
  labs(
    y = "Percent Best-Fit", x = "Group", fill = "Weight of acoustics",
    title = "Structural Alpha"
  ) +
  theme_few() +
  scale_fill_paletteer_d("colorBlindness::Blue2Orange12Steps") +
  theme(
    plot.title = element_text(hjust = 0.5),
    axis.text.x  = element_text(face = "bold")
  )
 

#PROCESS
#multimodaldelta switch betas
switch_prop <- best_blended_delta_bic_analysis %>%
  mutate(param1 = as.character(param1)) %>%
  group_by(Group, domain) %>%
  count(Group, domain, param1, name = "n") %>%         
  mutate(prop = n / sum(n)) %>%                        
  ungroup()

switch_alpha_plot<-ggplot(switch_prop, aes(x = Group, y = prop, fill = param1)) +
  geom_col(position = position_dodge2(width = 0.8, preserve = "single"), width = 0.75) +
  facet_wrap(~ domain) +
  scale_y_continuous(
    labels = percent_format(accuracy = 1),
    expand  = expansion(mult = c(0, 0.05))
  ) +
  labs(
    y = "Percent Best-Fit", x = "Group",
    fill = "Semantic weight",
    title = "Multimodal Switch Beta"
  ) +
  theme_few() +
  scale_fill_custom 
  theme(
    plot.title = element_text(hjust = 0.5),
    axis.text.x = element_text(face = "bold"))

#best model
model_prop <-
  best_blended_delta_bic_analysis %>%
  group_by(Group, domain) %>%
  count(Group, domain, model_type, name = "n") %>%
  mutate(prop = n / sum(n)) %>%
  ungroup()


model_plot<-ggplot(model_prop,aes(x = Group, y = prop, fill = model_type)) +
  geom_col(
    position = position_dodge2(width = 0.8, preserve = "single"),
    width = 0.75
  ) +
  facet_wrap(~ domain) +
  scale_y_continuous(labels = percent_format(accuracy = 1),
                     expand = expansion(mult = c(0, 0.05))) +
  labs(
    y = "Percent Best-Fit", x = "Group",
    fill = "Model",
    title = "Best-fit Model"
  ) +
  theme_few() +
  scale_fill_paletteer_d("rcartocolor::DarkMint") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(face = "bold"))


```

## Lexical & Clustering Analyses

## Overall Lexical - Domain differences
```{r}
#setting up lexical df 
lexical_analysis_data <-full_indv_data %>% select(SID, Group,Phonological_Similarity_mean, Frequency_Value_mean, 
         fluency_score, domain) %>% na.omit() %>% left_join(best_blended_delta_bic %>% select(SID,domain,Group,alpha)) %>%mutate(alpha=as.numeric(as.character(alpha)))%>%
  rename("phonological" = "Phonological_Similarity_mean",
         "frequency" = "Frequency_Value_mean")%>%
  pivot_longer(names_to = "cue", cols=c(phonological,frequency))%>%mutate(Group = factor(Group, levels = c("NH","CI"))) %>% unique()%>%
  filter(!(SID %in% c("332053124","722249212","826471010","934821408","566255711","588241255"))) #removing participants within missing demo info

#setting up the semantic df 
#using each participants best semantic structure
lexical_analysis_data_semantic<-best_blended_delta_bic_analysis%>%
  left_join(full_indv_data%>%mutate(alpha=as.numeric(alpha)) %>%select(SID,Group,domain,structure,dimension,alpha,Semantic_Similarity_mean)%>%na.omit())%>% mutate(Group = factor(Group, levels = c("NH", "CI")))


#Basic domain differences in lexical metrics
domain_semantic<- lm(Semantic_Similarity_mean ~ domain, data = lexical_analysis_data_semantic)
summary(domain_semantic)
#sig higher avg semantic similarity for foods

domain_phon<- lm(value ~ domain, data = lexical_analysis_data%>%filter(cue=="phonological"))
summary(domain_phon)
#sig higher avg phon similarity for foods

domain_freq<- lm(value ~ domain, data = lexical_analysis_data%>%filter(cue=="frequency"))
summary(domain_freq)
#sig higher avg freq for foods

```

## Word Stem Analyses
```{r}
#First pass each raw fluency txt file to phonemes.py

#Upload data
animals_phonemes<-read.csv("animals_phoneme_pairs.csv") %>%mutate(domain="animals")
foods_phonemes<-read.csv("foods_phoneme_pairs.csv")%>%mutate(domain="foods")
phonemes<-rbind(animals_phonemes,foods_phonemes)%>% rename(SID="ID") %>%left_join(participant_groupings)%>%filter(!(SID %in% c("332053124","722249212","826471010","934821408","566255711","588241255")))%>%filter(Word1 != Word2) #filter out atypical/missing demo SIDs 

#get list of words w/ shared stems
phonemes_stem<-phonemes%>%
  filter(Shared_Cont_Phonemes > 2) %>%
  arrange(SID, Group, domain) %>%
  filter(lag(Word2) != Word1 | is.na(lag(Word2))) %>%  # keep only if not repeated
  select(SID, Group, domain, Word1, Word2)%>%
  pivot_longer(cols = c(Word1, Word2),
               names_to = "Word_Type",
               values_to = "Word") %>%
  select(-Word_Type) %>%rename(entry="Word")
#overall
phoneme_all <- phonemes %>%
  summarize(
    count_cont = sum(Shared_Cont_Phonemes > 2, na.rm = TRUE),
    total = n(),
    proportion_stems = count_cont / total,
    avg_shared_length = mean(Shared_Cont_Phonemes, na.rm = TRUE)) %>%
  ungroup()
phoneme_all 

#by domain
phoneme_domain <- phonemes %>%
  group_by(domain) %>%
   summarize(
    count_cont = sum(Shared_Cont_Phonemes > 2, na.rm = TRUE),
    total = n(),
    proportion_stems = count_cont / total,
    avg_shared_length = mean(Shared_Cont_Phonemes, na.rm = TRUE),
    sd_shared_length = sd(Shared_Cont_Phonemes, na.rm = TRUE)) %>%
  ungroup()
phoneme_domain 


# Suppplementary Materials A

# taking out words w shared stems to see if lexical analyses change
# run after switches_recoded below

#import corrections to link to replacements
#library(readxl)
#animals_repl <- read_excel("../data/lexical_data/animals/corrections.xlsx") %>%
#  mutate(domain = "animals")
#foods_repl <- read_excel("../data/lexical_data/foods/corrections.xlsx") %>%
#  mutate(domain = "foods")

#comb_repl <- bind_rows(animals_repl, foods_repl) 


#comb_phonemes <- phonemes_stem %>%
#  left_join(comb_repl, by = c("entry", "domain"), relationship = "many-to-many") %>%
#  mutate(entry = if_else(!is.na(replacement), replacement, entry))

#switches_filtered <- switches_recoded %>% rename(entry="Fluency_Item")%>%
#  anti_join(
#    comb_phonemes %>% select(SID, entry),
 #   by = c("SID", "entry"))

#switch_no_stem_results <- switches_filtered  %>%mutate(Group = factor(Group, levels = c("NH","CI")))%>%
#  group_by(cue) %>%                                   
#  nest() %>%                                         
# mutate(
#    model = map(data, ~ lm(value ~ Group*domain*Switch*fluency_score, data = .)) 
#  )

#View results
#print("phonological")
#switch_no_stem_results$model[[2]] %>% summary()
#emmeans(switch_no_stem_results$model[[2]],pairwise~Group*domain*Switch,simple="Group",pbkrtest.limit = 35657)
#emmeans(switch_no_stem_results$model[[2]],pairwise~Group*Switch*fluency_score,simple="Switch",pbkrtest.limit = 35657) 

# looking at 3 way intx - does magnitude of difference between switch designations differ across groups in either domain
#mod <- switch_results$model[[2]]
#emm_domain <- emmeans(mod, ~ Group * domain * Switch, by = "domain")
#contrast(emm_domain, interaction = "pairwise") 


```

#Cluster Size & Number of Switches
```{r}
#filtering to only include indv best model from above
best_clusters <- full_indv_data %>%mutate(Group = factor(Group, levels = c("NH","CI")))%>%
  filter(paste(SID,Group,domain,full_method,dimension,structure,alpha) %in% paste(best_blended_delta_bic$SID,best_blended_delta_bic$Group,best_blended_delta_bic$domain, best_blended_delta_bic$full_method,best_blended_delta_bic$dimension,best_blended_delta_bic$structure,best_blended_delta_bic$alpha)) %>%select(-fluency_score)%>% #this is full of NAs & produces mismatch .x/.y error, so dropping
  group_by(SID,Group,domain) %>%left_join(lexical_analysis_data%>%select(SID,Group,domain,fluency_score)%>%unique(), by = c("SID", "Group","domain")) #adding fluency_score back in


#avg cluster size
#number of items produced as a covariate
domain_cluster_size_lm = lm(data = best_clusters, Cluster_Size_mean ~ Group * domain * fluency_score)
summary(domain_cluster_size_lm)

#number of switches
domain_switch_numb_lm = lm(data = best_clusters, Number_of_Switches ~Group * domain * fluency_score)
summary(domain_switch_numb_lm)
#ME of fluency score
```


## Within Cluster vs Switch Lexical Analyses
```{r}
#filtering to only include best for each indv
best_switches <- full_switch_data %>%
  filter(paste(SID,Group,domain,full_method,dimension,structure,alpha) %in% paste(best_blended_delta_bic$SID,best_blended_delta_bic$Group,best_blended_delta_bic$domain, best_blended_delta_bic$full_method,best_blended_delta_bic$dimension,best_blended_delta_bic$structure,best_blended_delta_bic$alpha)) %>%
  mutate(Switch_Value = if_else(Switch_Value == 2, 1, Switch_Value))

#Calculate item_no consistently in all_lexical to use in joining
items_lexical_data <- full_lexical_data %>%filter(paste(SID,Group,domain,dimension,structure,alpha) %in% paste(best_blended_delta_bic$SID,best_blended_delta_bic$Group,best_blended_delta_bic$domain,best_blended_delta_bic$dimension,best_blended_delta_bic$structure, best_blended_delta_bic$alpha))%>%select(-structure,-dimension,-alpha)%>%
  group_by(SID, Group, domain) %>%
  mutate(row_id = row_number() - 1)  # Adjust row_id to start at 0 to account for first item

#set up the df
#this code drops the first item from each list, and if switch_value = 1, marked as a switch trial, if switch_value=1, marked as within cluster transition, also labels clusters and switches by ordinal position
#new first item only marked as within cluster if original switch_value==0
switches_recoded <- best_switches %>%
  group_by(SID,Group,domain) %>%
  mutate(
    Cluster_Number = cumsum(Switch_Value == 1),
    Switch = case_when(
      row_number() == 1 ~ "Within Cluster Transition",  # Changed to "Within Cluster Transition"
      Cluster_Number != lag(Cluster_Number) ~ "Switch Trial", # Adding cluster number
      TRUE ~ "Within Cluster Transition"
    )
  ) %>%
  mutate(Switch_Number = case_when(
    Switch == "Switch Trial" ~ Cluster_Number - 1,  # Adding switch number
    TRUE ~ NA_real_
  )) %>%
  group_by(SID,Group, domain) %>%
  mutate(row_id = row_number() - 1) %>%  # Adjusting row_id to start at 0 to be able to drop first item
  left_join(items_lexical_data, by = c("SID","Group", "Fluency_Item", "domain","row_id")) %>%
  rename(
    "semantic" = "Semantic_Similarity",
    "phonological" = "Phonological_Similarity",
    "frequency" = "Frequency_Value"
  ) %>% filter(row_id!=0)%>% #dropping first word of each list
  pivot_longer(names_to = "cue", cols = c(semantic, phonological, frequency))%>%mutate(Group = factor(Group, levels = c("NH","CI"))) %>%left_join(just_fluency)%>%
  rename("fluency_score"="N")
                                                                                       
# Analysis

## does cluster/switch designation predict semantic similarity, phonological similarity, and frequency for each Group x Domain
switch_results <- switches_recoded  %>%mutate(Group = factor(Group, levels = c("NH","CI")))%>%
  group_by(cue) %>%                                   
  nest() %>%                                         
 mutate(
    model = map(data, ~ lm(value ~ Group*domain*Switch*fluency_score, data = .)) 
  )

#View results
#large so calling indp
print("Semantic")
switch_results$model[[1]] %>% summary() 
emmeans(switch_results$model[[1]],pairwise~domain*Switch,simple="domain",pbkrtest.limit = 35657)

print("phonological")
switch_results$model[[2]] %>% summary()
emmeans(switch_results$model[[2]],pairwise~Group*domain*Switch,simple="Group",pbkrtest.limit = 35657)
emmeans(switch_results$model[[2]],pairwise~Group*Switch*fluency_score,simple="Switch",pbkrtest.limit = 35657) 

# looking at 3 way intx - does magnitude of difference between switch designations differ across groups in either domain
mod <- switch_results$model[[2]]
emm_domain <- emmeans(mod, ~ Group * Switch, by = "domain")
contrast(emm_domain, interaction = "pairwise")

print("Frequency")
switch_results$model[[3]] %>% summary()
emmeans(switch_results$model[[3]],pairwise~domain*Group,pbkrtest.limit = 35657)

#correlation between semantic x phonological similarity in each domain
#on an item level
switches_recoded_corr<-switches_recoded %>% pivot_wider(names_from = cue, values_from = value)%>% select(SID, Group, Fluency_Item,semantic, phonological, frequency,domain) %>% na.omit() %>%mutate(Group = factor(Group, levels = c("NH","CI")))

sem_phon_model<-lm(data = switches_recoded_corr, semantic ~ phonological*Group*domain)
summary(sem_phon_model)
#sig intx of phonology x domain

```

### Within/Across Cluster plots
```{r}
#lexical metrics within vs across clusters
plots_switch<-switch_results %>% 
  mutate(
    emmip_plot = map(model, ~ 
      emmip(.x, Group ~ Switch | domain,  
            cov.reduce = range, CI = TRUE) +
      labs(title = "", x = "switch designation", y = paste("Estimated", unique(cue))) +facet_wrap(~domain) 
      +scale_colour_paletteer_d("nationalparkcolors::CraterLake")  +
      scale_fill_paletteer_d("nationalparkcolors::CraterLake") +
      theme_few() + 
      theme(legend.position = "top")))

plots_switch$emmip_plot[[3]]+
plots_switch$emmip_plot[[1]]+
plots_switch$emmip_plot[[2]]+
plot_layout(ncol = 1)

#intx of group x switch x fluency score for phonological similarity

ggplot(data=switches_recoded%>%filter(cue=="phonological")%>%mutate(Group = factor(Group, levels = c("NH","CI"))),aes(y = value, x = fluency_score, group = Switch, color = Switch)) + facet_wrap(~Group)+
  theme_few() +
  geom_smooth(method = "lm", se = TRUE,size=1) +
  theme(legend.position="top",
    aspect.ratio = 1,  
    axis.text.x = element_text( hjust = 1, face = "bold"))+scale_colour_paletteer_d("Manu::Kereru")+labs(y = "phonological similarity", x = "fluency score")

```

